manuscript_analysis_clean

### 2021-08-08 script/manuscript_clean_061021.Rmd
Update manuscript_clean_061021.Rmd
Updated outlier removal for by trial RT data frame. Outliers were already removed from the data file read into the script. The function to remove outliers from the by trial RT data was not necessary.

## Preprocess by trial RT data, remove the RT Slope outliers
```{r, include = F}
rt_trial <- read.csv("rt_trial.csv")

@@

    if (length(part_id) != 0) {
      rt_trial[-which(rt_trial$id %in% part_id & rt_trial$task == task), ]
    }
    return(rt_trial)
  }

@@

# Count N for each task
rt_trial %>%
  group_by(group, task) %>%
  filter(!is.na(reaction_time)) %>%
  summarize(n = length(unique(id))) %>%
  slice(match(c("lsl", "ssl", "vsl", "tsl"), task))
```

@@

## SL Cross-sectional Development Analyses: Post-hoc t-test of Linguistic SL Composite Scores in each age group
```{r}
# Younger group:
t.test(compositeAgeTDY$composite_ling, compositeAgeASDY$composite_ling, alternative = "greater")
# Older group:
t.test(compositeAgeTDO$composite_ling, compositeAgeASDO$composite_ling, alternative = "greater")
```

>>>>

## Preprocess by trial RT data, remove the RT Slope outliers
```{r, include = F}
# Outliers already removed in the data file (just to double check the removal)
rt_trial <- read.csv("rt_trial.csv")

@@

    if (length(part_id) != 0) {
    rt_trial <- rt_trial[-which(rt_trial$id %in% part_id & rt_trial$task == task), ]
    }
    return(rt_trial)
  }

@@

# Count N for each task
rt_trial %>%
  group_by(group, task) %>%
  filter(!is.na(reaction_time)) %>%
  dplyr::summarise(n = length(unique(id))) %>%
  slice(match(c("lsl", "ssl", "vsl", "tsl"), task))
```

@@

## SL Cross-sectional Development Analyses: Post-hoc t-test of Linguistic and Nonlinguistic SL Composite Scores in older children
```{r}
# Older group linguistic:
t.test(compositeAgeTDO$composite_ling, compositeAgeASDO$composite_ling)
# Older group nonlinguistic
t.test(compositeAgeTDO$composite_nonling, compositeAgeASDO$composite_nonling)
```
